\documentclass[12pt,english]{article}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage[a4paper]{geometry}
\geometry{verbose,tmargin=1in,bmargin=1in,lmargin=1in,rmargin=1in}
\setlength{\parskip}{\smallskipamount}
\setlength{\parindent}{0pt}
\usepackage{array}


\makeatletter

\providecommand{\tabularnewline}{\\}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
\makeatother
\usepackage{lineno,setspace}
\usepackage{fancyhdr}
\usepackage{}
\pagestyle{fancy}
\usepackage[small,compact]{titlesec}
\usepackage[small,it]{caption}
\addtolength{\belowcaptionskip}{-3mm}
\addtolength{\abovecaptionskip}{-3mm}
\usepackage{hanging}
\usepackage{babel}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=blue,
}
 

\makeatother

\fancyhead{}
\renewcommand{\headrulewidth}{0pt}
\fancyfoot{}
\lfoot{Monroe CV}
%\cfoot{CV}
\rfoot{\thepage}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\begin {center}
{\huge J Grey Monroe}\tabularnewline
\today

\vspace{1em}

\begin{tabular}{>{\raggedright}p{3in}>{\raggedleft}p{3in}}
USDA-NIFA National Needs Fellow & Graduate Degree Program in Ecology\tabularnewline
 greymonroe@gmail.com &  Colorado State University \tabularnewline
Phone: 919.810.8800 & Fort Collins, CO 80523\tabularnewline
\end{tabular}
\href{https://greymonroe.github.io}{https://greymonroe.github.io}
\end{center}
\vspace{-1em}

\rule[0.5ex]{1\columnwidth}{0.5pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\vspace{-.5ex}
\subsubsection*{EDUCATION}
\vspace{-0.5ex}

\hspace{1.0em} PhD, Ecology
\hfill 
2019 (expected)
\par
\hspace*{2.0em} Colorado State University, Fort Collins \\
\hspace*{2.0em} Advisor: John K. McKay \\
\hspace*{2.0em} Dissertation: The biology, genetics, and evolution of climate adaptation in plants 
\\
\vspace{-0.5ex}\par

\hspace{1.0em} BSc Biology, \emph{cum laude}  
\hfill
2012
\par
\hspace*{2.0em} Appalachian State University \\
\hspace*{2.0em} Advisor: Matt Estep \\
\hspace*{2.0em} Concentration: Evolution of centromeres in the \textit{Andropogoneae} \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{EMPLOYMENT}
\vspace{-0.5ex}\par

\hspace{1.0em} R Developer and Data Analyst
\hfill 
2017-2018
\vspace{-0.5ex}\par
\hspace{2.0em} United States Geological Survey
\vspace{-0.5ex}\par
\hspace{2.0em} John Wesley Powell Center for Analysis and Synthesis, Fort Collins, CO
\hfill 
\vspace{0.5em}\par

\hspace{1.0em} CO-OP in Plant Breeding and Genetics
\hfill 
2016 - 2017
\vspace{-0.5ex}\par
\hspace{2.0em} Cargill
\vspace{-0.5ex}\par
\hspace{2.0em} Specialty Seeds and Oil Innovation Center, Fort Collins, CO
\vspace{0.5em}\par

\hspace{1.0em} Research Assistant
\hfill 
2013 - 2014
\vspace{-0.5ex}\par
\hspace{2.0em} Duke University, Durham, NC
\vspace{-0.5ex}\par
\hspace{2.0em} Herman Staats Lab, Pathology Dept

\vspace{0.5em}\par

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection*{PUBLICATIONS}
\vspace{-0.5ex}

\begin{hangparas}{.5in}{1}

\hspace{1em} \textbf{Monroe JG}, Powell T, Price N, Howard A, Evans K, Mullen JL, Lovell JT, McKay JK. 2018. Drought adaptation in nature by extensive genetic loss-of-function. \textit{biorxiv}. doi: https://doi.org/10.1101/372854
\vspace{1ex}\par
\hspace{1em} Endriss SB, Vahsen ML, Bitume EV, \textbf{Monroe JG}, Turner KG, Norton AP, Hufbauer RA. The importance of growing up: juvenile environment influences dispersal of individuals and their neighbors. \textit{Ecology Letters}. in review
\vspace{1ex}\par
\hspace{1em} Dittberner H, Korte A, Mettler-Altman T, Weber A, \textbf{Monroe JG}, de Meaux J. 2018. Natural variation in stomata size contributes to the local adaptation of water-use efficiency in \textit{Arabidopsis thaliana}. \textit{Molecular Ecology}. in press
\vspace{1ex}\par
\hspace{1em}  Price N, Moyers BT, Lasky JR, \textbf{Monroe JG}, Mullen JL, Lopez L, Oakley CG, Lin J, Agren J, Schrider DR, Kern AD, McKay JK. 2018. Combining population genomics and fitness QTL to identify the genetics of local adaptation in \textit{Arabidopsis thaliana}. \textit{PNAS}. 115:5028-5033.
\vspace{1ex}\par
\hspace{1em}  \textbf{Monroe JG}, Markman DW, Beck WS, Felton AJ, Vahsen ML, Pressler Y. 2018. Eco-evolutionary Dynamics of Carbon Cycling in the Anthropocene. \textit{Trends in Ecology and Evolution}. 33:213-225.
\vspace{1ex}\par
\hspace{1em}  \textbf{Monroe JG}, Allen ZA, Tanger P, Mullen JL, Lovell JT, Moyers BT, Whitley D, McKay JK. 2017. \textit{TSPmap}, a tool making use of traveling salesperson problem solvers in the efficient and accurate construction of high-density genetic linkage maps. \textit{BioData Mining}. DOI 10.1186/s13040-017-0158-0.
\vspace{1ex}\par
\hspace{1em} Rockenbach K, Havrid JC, \textbf{Monroe JG}, Triant DA, Taylor DR, Sloan DB. 2016. Positive Selection in Rapidly Evolving Plastid-Nuclear Enzyme Complexes. \textit{Genetics} 204:1507-1522.
\vspace{1ex}\par
\hspace{1em} \textbf{Monroe JG}, McGovern C, Lasky J, Beck J, Grogan K, McKay JK. 2016. Adaptation to warmer climates by parallel functional evolution of \textit{CBF} genes in \textit{Arabidopsis thaliana}. \textit{Molecular Ecology} 15:3632-3644.
\vspace{1ex}\par
\hspace{1em} Mojica JP, Mullen J, Lovell JT, \textbf{Monroe JG}, Paul JR, Oakley CG, McKay JK. 2016. Genetics of water use physiology in locally adapted \textit{Arabidopsis thaliana}. \textit{Plant Science}  251:12-22.
\vspace{1ex}\par
\hspace{1em} Zhu M, \textbf{Monroe JG}, Suhail Y, Villiers F, Mullen J, Pater D, Hauser F, Jeon BW, Bader JS, Kwak JM, Schroeder JI, McKay JK, Assman SM. 2016. Molecular and Systems Approaches towards Drought-tolerant Canola Crops. \textit{New Phytologist} 210:1169-1189.
\end{hangparas}
\vspace{1ex}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection*{FELLOWSHIPS}
\vspace{-0.5ex}
\hspace*{1.0em} Vice President of Research Fellowship, CSU (\$4,000)
\hfill 
2017 - 2018
\vspace{1ex}\\
\hspace*{1.0em} USDA-NIFA National Needs Fellowship (\$138,000)
\hfill 
2015 - 2018
\vspace{1ex}\\
\hspace*{1.0em} Program in Molecular Plant Biology Fellowship, CSU (\$39,000)
\hfill 
2014 - 2015
\vspace{1ex}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{GRANTS}
\vspace{-0.5ex}
\hspace*{1.0em} Research Mentoring to Advance Inclusivity in STEM, CSU (\$1,160)
\hfill 
2018\vspace{1ex}\\
\hspace*{1.0em} Doctoral Dissertation Improvement Grant, NSF (\$19,760)
\hfill 
2017\\
\hspace*{2.0em} Title: The evolution of plant drought tolerance and gene function across\\
\hspace*{2.0em} historic drought frequency gradients 
\vspace{1ex}\\
\hspace*{1.0em} Evo-Devo-Eco Network Grant, Harvard University (\$3,000)
\hfill 
2016\\
\hspace*{2.0em} Title: Variation  in  developmental  and  physiological  responses  to  a  gradient\\ \hspace*{2.0em} of water availability in \textit{Brachypodium} 
\vspace{1ex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{AWARDS AND HONORS}
\vspace{-0.5ex}
\hspace*{1.0em} Graduate Degree Program in Ecology Travel Award, CSU (\$500)
\hfill 
2017
\vspace{1ex}\\
\hspace*{1.0em} Ralph Baker Graduate Student Award for Research Excellence, CSU (\$500)
\hfill 
2017
\vspace{1ex}\\
\hspace*{1.0em} NSF Graduate Research Fellowship (Honorable Mention)
\hfill 
2016
\vspace{1ex}\\
\hspace*{1.0em} Ralph Baker Graduate Student Award for Research Excellence, CSU (\$500)
\hfill 
2016
\vspace{1ex}\\
\hspace*{1.0em} PMPB Research and Scholarly Excellence Award, CSU (\$10,000)
\hfill 
2015
\vspace{1ex}\\
\hspace*{1.0em} NSF Graduate Research Fellowship (Honorable Mention)
\hfill 
2015
\vspace{1ex}\\
\hspace*{1.0em} GDPE Research and Scholarly Excellence Award, CSU (\$2,500)
\hfill 
2014
\vspace{1ex}\\
\hspace*{1.0em}  Frontiers and Techniques in Plant Science Workshop Scholarship,\\ 
\hspace*{1.0em} Cold Spring Harbor Laboratory   (\$750)
\hfill 
2014
\vspace{1ex}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{WORKSHOPS, WORKING GROUPS AND TRAINING}
\vspace{-0.5ex}
\hspace*{1.0em} Research Intern, Drought Physiology group
\hfill 
2018
\vspace{1ex}\\
\hspace*{2.0em}  International Rice Research Institute, Los Banos, Philippines
\vspace{1ex}\\
\hspace*{1.0em} Genotype $\times$ Environment Interactions Workshop, participant
\hfill 
2015
\vspace{1ex}\\
\hspace*{2.0em}  Wageningen University, Wageningen, Netherlands
\vspace{1ex}\\
\hspace*{1.0em} microMORPH Phenotypic Plasticity Workshop, invited participant
\hfill 
2015
\vspace{1ex}\\
\hspace*{2.0em}  Harvard University Arnold Arboretum, Boston, MA
\vspace{1ex}\\
\hspace*{1.0em} Plasticity and Novel Environments Working Group, invited participant
\hfill 
2015
\vspace{1ex}\\
\hspace*{2.0em}  National Evolutionary Synthesis Center, Durham, NC
\vspace{1ex}\\
\hspace*{1.0em} Frontiers and Techniques in Plant Science, invited participant
\hfill 
2014
\vspace{1ex}\\
\hspace*{2.0em}  Cold Spring Harbor Laboratory, Cold Spring Harbor, NY
\vspace{1ex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{PRESENTATIONS}
\vspace{-0.5ex}
\begin{hangparas}{.5in}{1}
\hspace{1em}\textbf{Monroe JG}. 2018. Drought adaptation by extensive genetic loss-of-function \textbf{(invited)}. Pennsylvania State Univeristy. State College, PA
\vspace{0.5ex}\par
\hspace{1em}\textbf{Monroe JG}. 2018. Drought adaptation by extensive genetic loss-of-function \textbf{(invited)}. Emerging Technologies to Prevent Future Famines Symposium. Fort Collins, CO
\vspace{0.5ex}\par
\hspace{1em}\textbf{Monroe JG}. 2018. Emerging technologies to discover beneficial gene knockouts for climate adaptation \textbf{(invited)}. International Rice Research Institute. Los Banos, Philippines
\vspace{0.5ex}\par
\hspace{1em}\textbf{Monroe JG}. 2018. From satellites to sequences: Discovering molecular targets of adaptation to remotely sensed drought histories \textbf{(invited)}. Australian National University. Canberra, Australia
\vspace{0.5ex}\par
\hspace{1em}\textbf{Monroe JG}. 2017. Plant adaptation to climate: environments, phenotypes, genes \textbf{(invited)}. Duke University. Durham, NC
\vspace{0.5ex}\par
\hspace{1em}\textbf{Monroe JG}. 2017. Plant adaptation to climate: environments, phenotypes, genes \textbf{(invited)}. Appalachian State University. Boone, NC
\vspace{0.5ex}\par
\hspace{1em}\textbf{Monroe JG}. 2017. Next-Generation Drought Detection and Whole Genome Sequences to Study Adaptation in \textit{Arabidopsis thaliana} (poster). Dupont-Pioneer Drought Tolerance Symyposium. Fort Collins, CO.
\vspace{0.5ex}\par
\hspace{1em}\textbf{Monroe JG}. 2017. Plant adaptation along historic drought frequency gradients. Evolution 2017. Portland, OR.
\vspace{0.5ex}\par
\hspace{1em}\textbf{Monroe JG}. 2017. The evolution of an important life history trait predicted by remote sensed drought frequency. Front Range Student Ecology Symposium. Fort Collins, CO.
\vspace{0.5ex}\par
\hspace{1em}\textbf{Monroe JG}. 2017. Using Nature to Nurture: uncovering the evolution of drought tolerance in wild plants. Three Minute Thesis Competition. Fort Collins, CO.
\vspace{0.5ex}\par
\hspace{1em}\textbf{Monroe JG}. 2016. Evolution of drought tolerance explored using global drought frequency map (poster). Graduate Student Showcase. Fort Collins, CO.
\vspace{0.5ex}\par
\hspace{1em}\textbf{Monroe JG}. 2016. A global map of drought frequency using the Vegetative Health Index (poster). Genomics of Adaptation to Human Contexts. Fort Collins, CO.
\vspace{0.5ex}\par
\hspace{1em}\textbf{Monroe JG}. 2016. Adaptation to warmer climates by parallel molecular evolution. Evolution 2016. Austin, TX.
\vspace{0.5ex}\par
\hspace{1em}\textbf{Monroe JG}. 2015. Patterns of locally adaptive altered function and divergence in cold response genes along a temperature gradient in Arabidopsis thaliana. Guild of Rocky Mountain Ecologists and Evolutionary Biologists. Boulder, CO.
\vspace{0.5ex}\par
\hspace{1em}\textbf{Monroe JG}. 2015. Evolution of the ABA signaling pathway in the Brassicaceae (poster). Evolution 2015. Sao Paolo, Brazil.
\vspace{0.5ex}\par
\hspace{1em}\textbf{Monroe JG}. 2015. Environmental variability and the evolution of locally adaptive drought responses. MicroMOPRH Phenotypic Plasticity Workshop. Harvard Arnold Arboretum. Boston, MA.
\vspace{0.5ex}\par
\hspace{1em}\textbf{Monroe JG}. 2015. Teaching plasticity by experiment: "EnvironMentoring" of a high school student (lightening talk) National Evolutionary Synthesis Center Plasticity and Novel Environments Working Group. Durham, NC.
\vspace{0.5ex}\par
\end{hangparas}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{TEACHING}
\vspace{-0.5ex}\par
\hspace*{1.0em} Guest lecturer
\par
\hspace*{2.0em} Drought Tolerance Breeding Workshop, CSU
\hfill 
2018
\par
\vspace{0.5em}
\hspace*{1.0em} Guest lecturer
\par
\hspace*{2.0em} Ecosystem Ecology, CSU
\hfill 
2017
\par
\vspace{0.5em}
\hspace*{1.0em} Teaching Assistant 
\par
\hspace*{2.0em} Molecular and General Genetics, CSU
\hfill 
2017
\par
\vspace{0.5em}
\hspace*{1.0em} Assistant Instructor
\par
\hspace*{2.0em} Software Carpentry Workshop, CSU
\hfill 
2016
\par
\vspace{0.5em}
\hspace*{1.0em} Guest lecturer
\par
\hspace*{2.0em} ECOL 592: Principles of Data Visualization Using R and ggplot2, CSU
\hfill 
2016
\vspace{0.5em}
\par
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{MENTORSHIP}
\vspace{-0.5ex}\par

\hspace*{1.0em} Karter Johansen -  theoretical population genetics of poly-allelic adaptation  
\hfill 
2017\\
\hspace*{2.0em} Colorado State University

\hspace*{1.0em} Tyler Powell - reverse genetics of adaptive loss-of-function alleles
\hfill 
2017\\
\hspace*{2.0em} Colorado State University

\hspace*{1.0em} Julio Flores - awarded scholarship for research on plant ecotoxicology 
\hfill 
2014-2015\\
\hspace*{2.0em} Poudre High School
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{ACADEMIC SERVICE}
\vspace{-0.5ex}\par

\hspace*{1.0em} Lecturer: Implicit Bias
\par
\hspace*{2.0em} CSU Research Mentoring to Advance Inclusiveness in Science
\hfill 
2018

\hspace*{1.0em} Assistant organizer
\par
\hspace*{2.0em} BSURE Undergraduate Summer Mentorship Program
\hfill 
2017

\hspace*{1.0em} Co-organizer
\par
\hspace*{2.0em} Drought Tolerance in Agriculture and Natural Ecosystems Symposium
\hfill 
2017
\hspace*{2.0em} DuPont-Pioneer and Colorado State University
\par
\vspace{0.5em}
\hspace*{1.0em} Assistant Organizer
\par
\hspace*{2.0em} Front Range Student Ecology Symposium
\hfill 
2015, 2017\\
\hspace*{2.0em} Graduate Degree Program in Ecology and Colorado State University
\par
\hspace*{1.0em} Peer Review
\par
\hspace*{2.0em} Evolution, New Phytologist, Theoretical and Applied Genetics, Evolutionary Applications, Scientific Reports

\vspace{0.5em}\par


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{SOFTWARE DEVELOPMENT}
\vspace{-0.5ex}

\begin{hangparas}{.5in}{1}
\hspace{1em}\textbf{J Grey Monroe}. soilcarbon: R package for interacting with Soil Radiocarbon Database\vspace{0.5ex}\par
\hspace{1em}\textbf{J Grey Monroe}. genemodel: Gene Model Plotting in R. R package version 1.1.0.
  https://CRAN.R-project.org/package=genemodel
\vspace{0.5ex}\par
\hspace{1em}\textbf{J Grey Monroe}., Zachary Allen, Paul Tanger, Brook Moyers and Jack Mullen (2016). TSPmap: A Method Making Use of Traveling Salesperson Problem Solvers in the Construction of Genetic Linkage Maps. R package version 0.0.0.9000. \\https://github.com/mckaylab/tspmap

\end{hangparas}

\end{document}
